BERT Model Compression and Weight Sharing

### 2019-05-11 paper/paper.tex
Fix citation style

We are interested in compressing the language representation model BERT \cite{devlin2018bert}. It is the state-of-art result in many natural language processing tasks such as natural language inference, paraphrasing and named entity recognition.

\cite{cheng2017survey} provides a comprehensive overview of the state-of-art methods to compress DNNs. Of the methods summarized by the paper, the ones that are of interest to our work are weight-pruning and quantization \cite{han2015deep}, and low-rank factorization \cite{denton2014exploiting}. Knowledge distillation, first proposed by \cite{bucilua2006model} as ``knowledge transfer'', was recently popularized by \cite{hinton2015distilling}. It differs from the previously mentioned methods since it compresses an existing model by replacing it with a simpler model that is trained on its outputs.

DeepTwist, a end-to-end training framework, allows us to incorporate compression procedures into training \cite{lee2018deeptwist}. Under this framework, the model parameters are occasionally distorted during training time instead of only at the end. This framework has the benefit of simplified training procedure and faster convergence and reduced requirement for hyperparameter tuning. Experiment on MNIST dataset with DeepTwist shows that LeNet-5 and LeNet-300-100 models are able to retain predictive accuracy under high compression rate.

>>>>

We are interested in compressing the language representation model BERT \citep{devlin2018bert}. It is the state-of-art result in many natural language processing tasks such as natural language inference, paraphrasing and named entity recognition.

\citet{cheng2017survey} provides a comprehensive overview of the state-of-art methods to compress DNNs. Of the methods summarized by the paper, the ones that are of interest to our work are weight-pruning and quantization \citep{han2015deep}, and low-rank factorization \citep{denton2014exploiting}. Knowledge distillation, first proposed by \citet{bucilua2006model} as ``knowledge transfer'', was recently popularized by \citet{hinton2015distilling}. It differs from the previously mentioned methods since it compresses an existing model by replacing it with a simpler model that is trained on its outputs.

DeepTwist, a end-to-end training framework, allows us to incorporate compression procedures into training \citep{lee2018deeptwist}. Under this framework, the model parameters are occasionally distorted during training time instead of only at the end. This framework has the benefit of simplified training procedure and faster convergence and reduced requirement for hyperparameter tuning. Experiment on MNIST dataset with DeepTwist shows that LeNet-5 and LeNet-300-100 models are able to retain predictive accuracy under high compression rate.
